gij bent 2

### 2025-10-01 paper/paper.qmd
Rewrite conclusion

First, we wanted to investigate to what extent individuals differ in their linguistic behaviour from the "general" behaviour predicted from their dialect area and gender. We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch (CBD) with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors. By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on the aforementioned general factors like gender and dialect region. Through elastic net regression, a modern regression technique, deviations were found for `r non_eliminated_count %>% formatn` users in the dataset (`r removed_distribution_prop[["FALSE"]] %>% formatp` of authors). `r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were more innovative than expected from their profile, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were more conservative than expected. We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects. The Brabant region correct towards the innovative form, the other regions correct towards the conservative form. We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.

The consequences of our findings are twofold. In general, our results show that individual variation exists, and in fact is abundant in our case. This illustrates that an important dimension of variation is likely lost in traditional regression models. On a more specific level, the regional and geospatial patterns in our data show that if people deviate from the general patterns we expect, this deviation is not random. In a sense, it means that there is "second order variation", variation *within* the variation, so to say. The geospatial distribution also provides an opportunity to anticipate upcoming diffusion patterns. Of course, we should not treat these patterns as oracles, but they can be useful nonetheless.

@@

[[ de discussie mag best wat uitgebreider - nu wat te summier ]]

>>>>

First, we wanted to investigate to what extent individuals differ in their linguistic behaviour from the "general" behaviour predicted from their dialect area and gender. We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch (CBD) with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors. By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on the aforementioned general factors like gender and dialect region. Through elastic net regression, a modern regression technique, deviations were found for `r non_eliminated_count %>% formatn` users in the dataset (`r removed_distribution_prop[["FALSE"]] %>% formatp` of authors). `r innovative_count %>% formatn` (`r non_zero_distribution_prop[["innovative"]] %>% formatp`) were more innovative than expected from their profile, while `r conservative_count %>% formatn` (`r non_zero_distribution_prop[["conservative"]] %>% formatp`) were more conservative than expected. We analysed these deviations regionally, and found that the innovative corrections were mostly associated with the central Brabant region, while the conservative corrections were mostly associated with the other Flemish dialect regions. We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.

In general, these results show that individual variation exists, and in fact is abundant in our case. This illustrates that an important dimension of variation is likely lost in traditional regression models (i.e. the bi-modal distribution seen in @fig-coefficient-plots-1). In addition, we see that individual variation is also not random. When we look at the individual corrections geographically, we find innovative types near dialect borders, while conservative types are more isolated. In a sense, this means that there is "second order variation", variation *within* the variation, so to say. The geospatial distribution also provides an opportunity to anticipate upcoming diffusion patterns. Of course, we should not treat these patterns as oracles, but they can be useful nonetheless.

@@
